Supplemental Materials, Methods and Results

### 2021-05-09 supp.Rmd
Dealing with model convergence problems. Will focus on models that converge normally

##########
# Achromatic Contrast - dL
##########

  # Fit the interaction model
  DispBgrdAC <- lmer(dL ~ Population  + Background_pop + BodyRegion + (1|ID), data=DisplayBgrd)
  summary(DispBgrdAC)

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
  robust_localAdapt_DispBgrdAC <- clubSandwich::conf_int(DispBgrdAC, cluster = DisplayBgrd$ID, vcov =  "CR2")

  # Add Wald test to test signifiacnce of each factor, background and population using roust variance
  background_AC_Disp <- Wald_test(DispBgrdAC, constraints = constrain_zero(3), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

  Population_AC_Disp <- Wald_test(DispBgrdAC, constraints = constrain_zero(2), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

  BodyRegion_AC_Disp <- Wald_test(DispBgrdAC, constraints = constrain_zero(4:6), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

  # Planned contrast. Fit the model in a slightly different way ********** PROBLEMS HERE TO WORK OUT WITH CS
  DisplayBgrd$pop_back_region <- with(DisplayBgrd, interaction(Population, Background_pop, BodyRegion))
  DisplayBgrd_Hawaii <- DisplayBgrd %>% filter(Population == "Hawaii")
  DisplayBgrd_pop_back_region <- lmer(dL ~ pop_back_region + (1|ID), data = DisplayBgrd_Hawaii) 
  summary(DisplayBgrd_pop_back_region)

  robust_DisplayBgrd_pop_back_region <- clubSandwich::conf_int(DisplayBgrd_pop_back_region, 
                                                               cluster = DisplayBgrd_Hawaii$ID, 
                                                               vcov =  "CR2")

  # Contrasts hypothesis tests, but use RVE 
    result_DisplayBgrd_pop_back_region <- Wald_test(DisplayBgrd_pop_back_region, 
                                             constraints = constrain_pairwise(c(1:16)),
                                             vcov="CR2", tidy = TRUE)
    result_DisplayBgrd_pop_back$p_val_bonfer <- sapply(p.adjust(result_DisplayBgrd_pop_back$p_val, "bonferroni"),
                                                       function(x) p_value(x))

@@

  # Planned contrasts / hypothesis tests. Need to fit model a little differently
    CourtshipBgrd$pop_back_BR <- with(CourtshipBgrd, interaction(Population, Background_pop, BodyRegion))
    CourtshipBgrd_Hawaii <-CourtshipBgrd %>% filter(Population == "Hawaii")
    CourtshipBgrd_pop_back_BR <- lmer(dL ~ -1 + pop_back_BR + (1|ID), data = CourtshipBgrd_Hawaii)

@@

    # Contrasts hypothesis tests, but use RVE 
      result_CourtshipBgrd_pop_back_BR_CC <- Wald_test(CourtshipBgrd_pop_back_BR_CC, 
                                                   constraints = constrain_pairwise(c(1:8)),
                                                   cluster = CourtshipBgrd_Hawaii$ID,
                                                   vcov="CR2", tidy = TRUE)
      result_CourtshipBgrd_pop_backCC$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_backCC$p_val, "bonferroni"), function(x) p_value(x))

@@

         result_CourtshipBgrd_pop_backCC <- result_CourtshipBgrd_pop_back_BR_CC[
                                            grep(string, result_CourtshipBgrd_pop_back_BR_CC$hypothesis),]

>>>>

# We only really want to compar the Hawaiian population, so we can subset that data
  DisplayBgrd$pop_back_region <- with(DisplayBgrd, interaction(Population, Background_pop, BodyRegion))
           DisplayBgrd_Hawaii <- DisplayBgrd %>% filter(Population == "Hawaii")
##########
# Achromatic Contrast - dL
##########

  # Fit the interaction model
  DispBgrdAC_inter <- lmer(dL ~  Background_pop + BodyRegion + Background_pop : BodyRegion + (1|ID), data=DisplayBgrd_Hawaii)
  summary(DispBgrdAC_inter)

  # Main effercts
   DispBgrdAC_main <- lmer(dL ~  Background_pop + BodyRegion + (1|ID), data=DisplayBgrd_Hawaii)
  summary(DispBgrdAC_main)

  # Wald test of interaction; Not important, so we'll simplify and assume just additive effects. This makes sense when we look at the raw data.
  intearction_AC_Disp <- Wald_test(DispBgrdAC_inter, constraints = constrain_zero(6:8), 
                                  cluster = DisplayBgrd_Hawaii$ID, vcov = "CR2")

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE). Given that there is no interaction, we can just present the main effects model with teh figure. Plus wald tests
  robust_localAdapt_DispBgrdAC <- clubSandwich::conf_int(DispBgrdAC_main, cluster = DisplayBgrd_Hawaii$ID, vcov =  "CR2")

  # Add Wald test to test signifiacnce of each factor using roust variance 
  background_AC_Disp <- Wald_test(DispBgrdAC_main, constraints = constrain_zero(2), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

  BodyRegion_AC_Disp <- Wald_test(DispBgrdAC_main, constraints = constrain_zero(3:5), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

@@

  # Planned contrasts / hypothesis tests. Need to fit model a little differently
    CourtshipBgrd$pop_back_BR <- with(CourtshipBgrd, interaction(Population, Background_pop, BodyRegion))
         CourtshipBgrd_Hawaii <- CourtshipBgrd %>% filter(Population == "Hawaii")
    CourtshipBgrd_pop_back_BR <- lmer(dL ~ -1 + pop_back_BR + (1|ID), data = CourtshipBgrd_Hawaii)

@@

     # Contrasts hypothesis tests, but use RVE 
          result_CourtshipBgrd_pop_back_BR_CC <- Wald_test(CourtshipBgrd_pop_back_BR_CC, 
                                                   constraints = constrain_pairwise(c(1:8)),
                                                   cluster = CourtshipBgrd_Hawaii$ID,
                                                   vcov="CR2", tidy = TRUE)
             result_CourtshipBgrd_pop_back_BR_CC$p_val_bonfer <- sapply(p.adjust(result_CourtshipBgrd_pop_back_BR_CC$p_val, "bonferroni"), 
                                                                    function(x) p_value(x))

@@

         result_CourtshipBgrd_pop_back_BR_CC <- result_CourtshipBgrd_pop_back_BR_CC[
                                            grep(string, result_CourtshipBgrd_pop_back_BR_CC$hypothesis),]
